draftFiguresPaper

### 2025-10-24 draftFiguresPaper.Rmd
categories pol

summaryDataset$categoryPollution <- cut(summaryDataset$pm25Avg, breaks = c(0, 5, 10, 15, 25, 35, 100), 
                  labels = c("no pol", "very low", "low", "medium", "high", "very high"), 
                  right = FALSE)

>>>>

summaryDataset$categoryPollution <- cut(summaryDataset$pm25Avg, breaks = c(0, 10, 15, 25, 35, 100), 
                  labels = c("very low", "low", "medium", "high", "very high"), 
                  right = FALSE)
